Unsupervised embedding of trajectories captures the latent structure of mobility

### 2021-02-11 paper/current/main.tex
fix typo

There is an alternative implementation of \textit{word2vec} based on a matrix factorization~\cite{levy2014neural,Qiu2018}, which optimizes the same objective function as for \texttt{gensim} but in a different way.
The matrix factorization approach generates embedding vectors such that the dot similarity for locations $i$ and $j$ is as close as $q_{ij}= \log(T_{ij} / s_i s_j) + \text{const}$.
An issue is that the generated embedding vectors can be largely affected by small flows $T_{ij}$ in the data.
For example, if there is no flow between locations $i$ and $j$ (\ie, $T_{ij} = 0$), then $Q_{ij} = -\infty$, pushing $i$ and $j$ to the infinite horizon of the embedding space.
To remedy this problem, one can add a small amount of flow between such locations or exclude them from the embedding~\cite{levy2014neural,Qiu2018}.
However, this may change the data to which we fit the model, and small flows may still have profound impact on the embedding space.
Therefore, we adopt the \textt{gensim} implementation of the \textit{word2vec}.
Our simulations show that, in the prediction task of mobility flow, \texttt{gensim}'s word2vec performs better than the matrix factorization approach in xxx out of the xxx datasets (Fig.~??).

>>>>

There is an alternative implementation of \textit{word2vec} based on a matrix factorization~\cite{levy2014neural,Qiu2018}, which optimizes the same objective function as for \texttt{gensim} but in a different way.
The matrix factorization approach generates embedding vectors such that the dot similarity for locations $i$ and $j$ is as close as $q_{ij}= \log(T_{ij} / s_i s_j) + \text{const}$.
An issue is that the generated embedding vectors can be largely affected by small flows $T_{ij}$ in the data.
For example, if there is no flow between locations $i$ and $j$ (\ie, $T_{ij} = 0$), then $q_{ij} = -\infty$, pushing $i$ and $j$ to the infinite horizon of the embedding space.
To remedy this problem, one can add a small amount of flow between such locations or exclude them from the embedding~\cite{levy2014neural,Qiu2018}.
However, this may change the data to which we fit the model, and small flows may still have profound impact on the embedding space.
Therefore, we adopt the \textt{gensim} implementation of the \textit{word2vec}.
Our simulations show that, in the prediction task of mobility flow, \texttt{gensim}'s word2vec performs better than the matrix factorization approach in xxx out of the xxx datasets (Fig.~??).
